SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-18 frontrunning/Latex/sections/paper.tex
[forontrunning] fix ghazal citation

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot\footnote{\url{https://twitter.com/ensbot}}) or people can bid on domains even though they do not know what they are because of speculation on its value.

>>>>

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavi2018ghazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot\footnote{\url{https://twitter.com/ensbot}}) or people can bid on domains even though they do not know what they are because of speculation on its value.
